Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-13 report/report.tex
Fix title capitalization, analysis -> conclusions
Shorten long headlines and fix main text linebreaks

\section{Research Question}

@@

\subsection{Assesment of Geodata Precision}

@@

\section{Problem Constraints}

@@

\section{Background of 3D City Representation}

@@

\section{OSM Data}

@@

\section{SLU Data}

@@

\section{Specific preprocessing for SLU and OSM geodata}

@@

\chapter{Implemenation: Evaluation of the quality of geodata}

@@

\section{The accuracy classes that will not be focused on}

The lineage aspect of the OSM data is available through the OSM History Viewer, an online debugging tool that lets anyone freely view the change history of individual fetures in a commit history-like fashion. There is an option for editors to include a personal note with their changesets to include additional details or motivate why a change was made, but there is no guaratee that the data includes any information on the aquisition method used (OSM 2020). The history aspect of the SLU dataset is not freely available online, but the acquistion method is included in the file metadata on a per-object basis. Lantmäteriet uses internal codes to specifify the acquistion method, and these codes can be referred to in the product description the accompanies the map files. As the scope of this project is limited to making a broad comparison of the positional accuracy of the two datasets, only the required positional accuracy as described by the SLU product description will be used.

@@

The temporal accuracy will not be assessed as this projects focuses on comparing a single snapshot of the two datasets at the same point in time.

The logical accuracy will not be assessed because the underlying logical relations between features in both maps serve no purpose to this project.

\section{Assesment of dataset completeness}

@@

\section{Correspondence by building area}

@@

\section{Shape accuracy definition}

@@

\section{Closest point and point proximity}

@@

\chapter{Implementation: Collision study}

@@

\chapter{Analysis and Future Work}

@@

\section{Suggested algorithms for correcting feature overlap}

>>>>

\section{Research question}

@@

\subsection{Assesment of geodata precision}

@@

\section{Problem constraints}

@@

\section{Background of 3D city reproduction}

@@

\section{OSM data}

@@

\section{SLU data}

@@

\section{Specific geodata preprocessing}

@@

\chapter{Implementation}

\section{Geodata precision study}

\subsection{Quality criteria}

@@

\subsection{Other accuracy criteria}

Let us briefly go over all of van Oorts accuracy criteria that will not be assessed through this study.
Let us see how they could be obtained and assessed for both the OSM and SLU maps, staring with the data lineage.
The lineage aspect of the OSM data is available through the OSM History Viewer, an online debugging tool that lets anyone freely view the change history of individual fetures in a commit history-like fashion.
There is an option for editors to include a personal note with their changesets to include additional details or motivate why a change was made, but there is no guaratee that the data includes any information on the aquisition method used (OSM 2020).
The history aspect of the SLU dataset is not freely available online, but the acquistion method is included in the file metadata on a per-object basis.
Lantmäteriet uses internal codes to specifify the acquistion method, and these codes can be referred to in the product description the accompanies the map files.
As the scope of this project is limited to making a broad comparison of the positional accuracy of the two datasets, only the required positional accuracy as described by the SLU product description will be used.

@@

The temporal accuracy will not be assessed as this projects focuses on comparing a single snapshot of the two datasets at the same point in time, and finally the logical accuracy will not be assessed because the underlying logical relations between features in both maps serve no purpose to this project.

\subsection{Assesment of dataset completeness}

@@

\subsection{Correspondence by building area}

@@

\subsection{Shape accuracy definition}

@@

\subsection{Closest point and point proximity}

@@

@@

\chapter{Conclusions and future work}

@@

\section{Suggested algorithms for collision correction}
